\documentclass[12pt,a4paper]{article}

% Packages
\usepackage[margin=1in,left=1.5in]{geometry}
\usepackage{times}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage[titles]{tocloft}
\usepackage{fancyhdr}
\usepackage[backend=bibtex,style=apa]{biblatex}

% Bibliography file
\addbibresource{references.bib}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}

% Section formatting
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}

% Table of contents formatting
\renewcommand{\cfttoctitlefont}{\hfill\Large\bfseries}
\renewcommand{\cftaftertoctitle}{\hfill}
\renewcommand{\cftsecfont}{\normalfont}
\renewcommand{\cftsecpagefont}{\normalfont}
\setlength{\cftbeforesecskip}{5pt}

\begin{document}

% Title page
\begin{titlepage}
\begin{center}
\vspace*{2cm}
{\huge\bfseries Project Proposal\par}
\vspace{1.5cm}
{\Large\bfseries Muwaqqit\par}
\vspace{2cm}
{\Large Submitted By\par}
\vspace{1cm}
{\Large\bfseries YAZED ALKHALAF - 202211123\par}
{\Large\bfseries SAIMAN TAKLAS - 202021400\par}
{\Large\bfseries AFFAN MOHAMMAD - 202211086\par}
\vfill
{\Large Supervised By: Dr. Inaya Allah\par}
\vspace{1cm}
{\Large Al Yamamah University\par}
{\Large College of Engineering and Architecture\par}
{\Large Bachelor of Science in Software and Network Engineering\par}
\vspace{1cm}
{\Large \today\par}
\end{center}
\end{titlepage}

% Table of Contents
\tableofcontents
\clearpage

% Main content
\pagenumbering{arabic}
\doublespacing

\section{Background of the Project}

- globalization
- time management

people usually want to use calendars, but they are not user-friendly. Especially when you have multiple calendars, work, school, personal, etc...

\section{Problem Statement}

- keeping track of your calendar and making sure it is up to date with all the data sources (whatsapp)

\section{Objectives of the Project}

- saving people time
- 

\section{Significance of the Project}
% Add your content here

\section{Scope of the Project}
% Add your content here

- decide priority from notification, the action thingy with two buttons.
- ask user for when they sleep, when they wake up, like time blocks in the day to put things around. hold times for things for you. excercises (gym) time.
- lunch hold automatically, makes sure to plan time for food.
- connect your academic schedule, the courses :D
- find me x minutes on y day
- automatic travel time based on location (lat, lng)
- suggest soemthing to eat in the food block.

\section{Limitations of the Project}
% Add your content here

- 

\section{Project Plan}
% Add your content here

\section{Literature Review}
% Add your content here

- https://www.getclockwise.com/
- 

\section{Conclusion}
% Add your content here

\printbibliography[title=References]

\end{document}