\begin{usecase}{Add Event Manually}
    \ucbasicinfo{High}{Regular}
    \ucshortdescription{This UC allows users to add events manually }
    \uctrigger{The user clicks and adds the events.}
    \ucactors{User}{None}
    \ucpreconditions{The user is logged into the application }
    \ucrelationships{N/Al}{N/A}{N/A}
    \ucinputsoutputs{
      \begin{itemize}
        \item \textbf{Event Name} (Source: User)
        \item \textbf{Event Location} (Source: User)
        \item \textbf{Event Date (Start and End)} (Source: User)
        \item \textbf{Event Time (Start and End)} (Source: User)
        \item \textbf{Event Description} (Source: User)
        \item \textbf{Notifications/Reminders} (Source: User)
      \end{itemize}
    }{
      \begin{itemize}
        \item \textbf{The event is displayed on the calendar with its details and duration
        } (Destination: Calendar)
      \end{itemize}
    }
    \ucmainflow{
      \begin{enumerate}
        \item The name of the event (e.g., ``Meeting with Client'')
          \ucinfo{Event is saved and displayed on the user’s calendar}
        \item The start and end time of the event.
          \ucinfo{The system displays the event in the correct time slot with its duration, while checking for conflicts and scheduling notifications}
        \item The User optionally adds a description
          \ucinfo{The system stores and displays description of the event.}
        \item Set reminders for the event.
          \ucinfo{Notification or reminder set for the event}
      \end{enumerate}
    }
    \ucalternateflows{
      \begin{enumerate}
        \item User clicks on a date on the calendar to bring up a popup with event fields and the date is pre-filled. 
        \item	The user can add a different color for the events.
      \end{enumerate}
    }
    \ucexceptions{
      \begin{itemize}
        \item Invalid date and time format\
        \item The event's start and end times conflict with an existing event
        \item The user attempts to save the event without filling in mandatory fields
      \end{itemize}
    }
    \ucconclusion{The UC ends when the event has been successfully added to the calendar, and the user sees it displayed.}
    \ucpostconditions{The event is successfully added to the calendar, visible in the correct time slot, and notifications are set as per user preferences}
    \ucspecialrequirements{The interface must be simple and allowing users to input events with less efforts.}
\end{usecase}