\begin{usecase}{Configure Daily Routine}
    \ucbasicinfo{HIGH}{Regular}
    \ucshortdescription{The use case starts when the user initiates the configuration or editing of their daily routine in the app.}
    \uctrigger{The user selects the "Daily Routine" feature to configure repetitive tasks like waking up, exercise, meals, and sleeping time.}
    \ucactors{User}{None}
    \ucpreconditions{The user is logged into the application }
    \ucrelationships{N/Al}{N/A}{N/A}
    \ucinputsoutputs{
      \begin{itemize}
        \item \textbf{Routine tasks (e.g., wake up, jog, meals, bath time, sleep)} (Source: User)
        \item \textbf{Start and end times for each task.} (Source: User)
        \item \textbf{Recurrence pattern (daily, weekdays, weekends, etc)} (Source: User)
        \item \textbf{Notifications or reminders (e.g., alarms for specific tasks).} (Source: User)
      \end{itemize}
    }{
      \begin{itemize}
        \item \textbf{The daily routine is added to the calendar with all configured tasks displayed as recurring events.} (Destination: Calendar)
      \end{itemize}
    }
    \ucmainflow{
      \begin{enumerate}
        \item The user adds Daily tasks (wake up, meals, sleep, etc.)
          \ucinfo{Routine tasks are added to the calendar.}
        \item The start and end time of the event.
          \ucinfo{The system displays the event in the correct time slot with its duration, while checking for conflicts and scheduling notifications}
      \end{enumerate}
    }
    \ucalternateflows{
      \begin{enumerate}
        \item The user clicks on the calendar, the system displays the daily routine tasks.
      \end{enumerate}
    }
    \ucexceptions{
      \begin{itemize}
        \item Conflict with tasks
      \end{itemize}
    }
    \ucconclusion{Configuring a daily routine enables users to block out dedicated time for recurring tasks.}
    \ucpostconditions{The daily routine is successfully configured and integrated into the calendar, with appropriate visual indicators and reminders.}
    \ucspecialrequirements{The interface must be simple and allowing users to have the daily routines Throughout.}
\end{usecase}