\begin{usecase}{Connect WhatsApp}
    \ucbasicinfo{High}{Regular}
    \ucshortdescription{This UC allows the user to connect their WhatsApp account to the system.}
    \uctrigger{This UC is triggered when the user clicks on ``Connect WhatsApp'' button in the app.}
    \ucactors{User}{WhatsApp}
    \ucpreconditions{User must be logged in}
    \ucrelationships{N/A}{N/A}{N/A}
    \ucinputsoutputs{
      \begin{itemize}
        \item \textbf{WhatsApp phone number} (Source: User)
        \item \textbf{WhatsApp linking code} (Source: User)
      \end{itemize}
    }{
      \begin{itemize}
        \item \textbf{WhatsApp auth credentials} (Destination: System)
      \end{itemize}
    }
    \ucmainflow{
      \begin{enumerate}
        \item The user clicks ``Connect WhatsApp'' button.
          \ucinfo{The system asks for the user's WhatsApp phone number.}
        \item The user enters their WhatsApp phone number.
          \ucinfo{WhatsApp shows the linking code in their app.}
        \item The user enters the linking code in our app.
          \ucinfo{The app shows a success screen if connection was sucessful.}
      \end{enumerate}
    }
    \ucalternateflows{
      \begin{enumerate}
        \item If the WhatsApp connection fails, the user must redo the steps and try again.
      \end{enumerate}
    }
    \ucexceptions{
      \begin{itemize}
        \item \textbf{Wrong linking code:} If the user enters a wrong linking code, the connection of the WhatsApp account will fail unless they enter the correct code.
        \item \textbf{Network issue:} A network issue interrupting the communication between the app, the server, and WhatsApp.
      \end{itemize}
    }
    \ucconclusion{The UC ends when the user has a connected WhatsApp account in the system.}
    \ucpostconditions{The system has access to the user's WhatsApp account.}
    \ucspecialrequirements{None}
\end{usecase}