\begin{usecase}{Continue with Email}
    \ucbasicinfo{HIGH}{Regular}
    \ucshortdescription{This UC allows users to login or create an account using their email.}
    \uctrigger{This UC starts when the user enters their email to the system.}
    \ucactors{User}{None}
    \ucpreconditions{User must have an email}
    \ucrelationships{Send Welcome Email}{N/A}{N/A}
    \ucinputsoutputs{
      \begin{itemize}
        \item \textbf{Email} (Source: User)
        \item \textbf{Magic Link (from email)} (Source: User)
      \end{itemize}
    }{
      \begin{itemize}
        \item \textbf{Magic link email} (Destination: User)
        \item \textbf{Confirmation messages} (Destination: User Interface)
      \end{itemize}
    }
    \ucmainflow{
      \begin{enumerate}
        \item The user enters their email.
          \ucinfo{System displays an email input field.}
        \item System generates and sends magic link.
          \ucinfo{System sends email and displays "Check your email" message}
        \item The user clicks the magic link.
          \ucinfo{The app is opened on the device of the user}
        \item The app sends the token to the system to log the user in
          \ucinfo{System verifies token and logs user in.}
      \end{enumerate}
    }
    \ucalternateflows{
      \begin{enumerate}
        \item If the user has no account, the system creates a user.
      \end{enumerate}
    }
    \ucexceptions{
      \begin{itemize}
        \item Invalid email format.
        \item Email not registered (if login only).
        \item Magic link token expired or invalid.
      \end{itemize}
    }
    \ucconclusion{This UC ends when the user is logged in.}
    \ucpostconditions{The system generates a JWT.}
    \ucspecialrequirements{An email server must be present to send magic link email.}
\end{usecase}