\begin{usecase}{Schedule Prayer Times}
    \ucbasicinfo{HIGH}{Regular}
    \ucshortdescription{Allows users to create, edit, and manage their prayer time schedules.}
    \uctrigger{User selects the option to schedule prayer times.}
    \ucactors{User}{None}
    \ucpreconditions{User must be logged into the system.}
    \ucrelationships{N/A}{N/A}{N/A}
    \ucinputsoutputs{
      \begin{itemize}
        \item \textbf{User's prayer time details} (Source: user)
        \item \textbf{(date, time)}
      \end{itemize}
    }{
      \begin{itemize}
        \item \textbf{Confirmation of scheduled prayer times, calendar entries.}
      \end{itemize}
    }
    \ucmainflow{
      \begin{enumerate}
        \item User navigates to the prayer scheduling page.
          \ucinfo{User is presented with a form to enter prayer times. Display of the scheduling interface.}
        \item User inputs prayer time details.
          \ucinfo{Input fields for time, date, and prayer type. User's input is captured for validation.}
        \item User saves the schedule.
          \ucinfo{System checks for valid input. Confirmation message displayed.}
        \item System confirms schedule creation.
          \ucinfo{User receives a notification. Scheduled prayer times are saved in the system.}
      \end{enumerate}
    }
    \ucalternateflows{
      \begin{itemize}
        \item If input is invalid, display error messages.
      \end{itemize}
    }
    \ucexceptions{
      \begin{itemize}
        \item If there's a system error, display a relevant error message.
      \end{itemize}
    }
    \ucpostconditions{The system generates calendar entries for the scheduled prayer times.}
    \ucspecialrequirements{The system must support notifications for prayer times.}
    \ucconclusion{User's prayer times are successfully scheduled.}
    \ucbusinessrules{
      \begin{itemize}
        \item Prayer times must be within valid time ranges.
      \end{itemize}
    }
\end{usecase}